\documentclass{article}
\begin{document}

\title{Development of LDL}

\author{Guohui Xiao}
	%\institute{KBS Group, TU Wien}

\newcommand{\La}{\Leftarrow}
\newcommand{\Ra}{\Rightarrow}

\maketitle

\section{Expressive Power}

\begin{itemize}
\item ObjectPropertyDomain

the domain of $R$ is $D$

%$R$ domain $D$
$\exists R.\top \sqsubseteq D$  $\Ra$ \verb|D(x) :- R(x,y).|

\item 
ObjectPropertyRange

the range of $R$ is $D$

$\top \sqsubseteq \forall R.D$ $\Ra$ \verb|D(y) :- R(x,y).|

\end{itemize}



\section{Extending OWL-API with More Role Constructors}

OWL API 3.0 is targeted on OWL 2 which is based on description logic
SROIQ.

In SROIQ, we do not have much role constructors.

We extend OWL-API
with the following role constructors:
\begin{itemize}
\item Role conjunction: LDLObjectPropertyIntersectionOf
\item Role intersection: LDLObjectPropertyUnionOf
\item Role transitive closure: LDLObjectPropertyTransitiveClosureOf
\item Role inversion: LDLObjectPropertyInversionOf
\item Role nominals: LDLObjectPropertyOneOf
\item Role chain: LDLObjectPropertyChainOf
\end{itemize}  Note that, in OWL2, we already have role inversion
and chain.  However, the syntaxes are very restricted.  In LDL, we
will release this, so we need to add new constructors.  Affected
java classes in owl-api 3.0: 
\begin{itemize}
\item org.coode.owlapi.rdfxml.parser
  \begin{itemize}
  \item class OWLRDFConsumer 
    \begin{itemize}
    \item objectPropertyExpressionTranslatorSelector (A)
    \item translatedObjectPropertyExpression (A)
    \item translateToObjectPropertyExpressionSet(IRI) (A)
    \item setupPredicateHandlers() (M)
      \begin{itemize}
      \item addPredicateHandler(new
        TPObjectPropertyTransitiveClosureOfHandler(this));
      \item addPredicateHandler(new
        TPObjectPropertyUnionOfHandler(this));
      \item addPredicateHandler(new
        TPObjectPropertyIntersectionOfHandler(this)); 
      \end{itemize}
    \end{itemize}
  \end{itemize}
\end{itemize}  

For every new constructor, we

\begin{itemize}

\item add LDLObjectPropertyChainOf
\item add LDLObjectPropertyChainOfImpl
\item add LDLObjectPropertyChainOfTranslator 
\item add TPObjectPropertyChainOfHandler (seems no use)
\item update ObjectPropertyExpressionTranslatorSelector
\item update OWLRDFVocabulary
\item update OWLDataFactoy
\item update OWLDataFactoryImpl
\item update OWLRDFConsumer 
\item update *Visitor
\end{itemize}

For inveseOf, which is already an OWL2 constructor, we
\begin{itemize}
\item add OWLObjectPropertyInverseOfTranslator
\item update ObjectPropertyExpressionTranslatorSelector
\end{itemize}

\section{DLV java wrapper}

The DLV Wrapper Project (http://www.mat.unical.it/wrapper/index.html) is
too old. It does not support latest DLV which support WFS.

So I decompiled the source code of DLV Java Wrapper 3.0 and read it.

Finally I wrote one.

\section{XSB java wrapper}

\subsection{JNI Mode}
\label{sec:XSB-jni}

To compile the 

Add the following line
\begin{verbatim}
#include <context.h>
\end{verbatim}
to the c files.
	
In XSBHello.java
\begin{verbatim}
    	String[] xsbargs= {"/home/staff/xiao/local/xsb/xsb3.2", 
    	"--noprompt", "--quietload"};
\end{verbatim}
	
To run XSBHello, we must add the following to the VM variables:
\begin{verbatim}
       -Djava.library.path=/home/staff/xiao/local/xsb/xsb3.2/lib:
/home/staff/xiao/local/xsb
\end{verbatim}
	
problem: 
\begin{itemize}
\item How to compile a class expression as a legal predicate?
\item Always crash!!
\end{itemize}

I have given it up :-(


\subsection{Sub-process Mode of Interprolog}

\begin{itemize}
\item Unexpected Exception
\item Report unfounded result as true
\end{itemize}

\subsection{My Sub-process Java Wrapper for XSB}

I implemented a sub-process java wrapper for XSB.

Using multi-threads to monitor the output (stderr, stdout) of the XSB
sub process.

\section{Evaluation}

\subsection{Other Reasoners and Evaluation}

\begin{itemize}
\item
  \begin{description}
    \item[Reasoner] KAON2    

    \item[Literature] Motik's PhD Thesis 

    \item[Ontology] VICODI, LUBM, Wine, Galen

    \item[Task] Querying Large ABoxes, TBox Classification
  \end{description}

\item
  \begin{description}
  \item[Reasoner] CEL
  \item[Literature] CEL—A Polynomial-time Reasoner for Life Science
    Ontologies
  \item[Ontology] Go, Galen, Snomed
  \item[Task] Classification
  \end{description}
\item
  \begin{description}
  \item[Reasoner] HermiT
  \item[Literature] HermiT: A Highly-Efficient OWL Reasoner
  \item[Ontology] Fly, GO, GALEN, ...
  \item[Task] Classification
  \end{description}

\item
  \begin{description}
  \item[Reasoner] Requiem
  \item[Literature] Efficient Query Answering for OWL 2
  \item[Ontology] VICODI, LUBM
  \item[Task] Query Rewriting
  \end{description}

\item
  \begin{description}
  \item[Reasoner] Pellet
  \item[Literature] Pellet: A Practical OWL-DL Reasoner
  \item[Ontology] AKT, Tambis, SUMO, Food, OWL-S, Financial, SWEEt,
    Wine, Galen
  \item[Ontology] Consistency Checking, Classification
  \end{description}
\item
  \begin{description}
  \item[Reasoner] DLVHex + dlplugin
  \item[Literature] Exploiting Conjunctive Queries in
  Description Logic Programs
\item[Ontology] Same with KAON2
\item[Task] Conjunctive Query for DL-program
\end{description}


\end{itemize}

\subsection{LUBM}
\label{sec:lubm}

Violated axioms:

$GraduateStudent \sqsubseteq \exists takesCourse.GraduateCourse$


\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% TeX-PDF-mode: t
%%% TeX-debug-bad-boxes: t
%%% TeX-master: t
%%% TeX-parse-self: t
%%% TeX-auto-save: t
%%% reftex-plug-into-AUCTeX: t
%%% End: 